Averaging subsampled pseudoinverses

### 2022-08-23 design/save/colt19/rebuttal.txt

### Review 1 ###
Title: Thanks for the good suggestions

>> " 'minimax optimal experimental design'  is really 'minimax optimal among all unbiased estimators', right?"
Good point! We will clarify the section and make it clear that
we are looking for minimax optimal 'unbiased' estimators

+++MW: Not done
You only changed the title of the section.
Change title seems to be too much now?
I stressed unbiasedness in abstract

>> "...why you restrict to unbiased estimators here"
The key advantage of using unbiased estimators for the
minimax definition is that we can say that the least
squares estimator w_LS is the minimum variance estimator
among them (Proposition 7). If we include all biased
estimators, then it is not clear what w_LS
should be replaced with to even define the minimax value. Also, unbiased estimators 
are closed under averaging and this immediately lets us
reduce the variance/loss. We will add more discussion to clarify this.

+++MW: not done
Added a minimal remark before Prop. 7 in Magenta

>> "how does this compare to the pseudo-sequential setting"
This setting gives more freedom to the design, so we would expect that the bounds should be at least as good. Certainly, this is a great direction for future work!

>> "I found it confusing that \hat{\bf w}({\bf y}_S ) is not written conditional on {\bf X}"
Good point! Of course the estimator function has to depend on X. Since X is fixed beforehand, and then w_hat is chosen afterwards, we treat the dependence on X as implicit in the choice of w_hat. We will clarify this point in the final version!

+++MW: not done
Sometimes with condition on X and sometimes we dont
Indeed confusing. See for example statement of Thm 4
Would be hard to fix though

hat w (y_S)   but  w_LS(y|X)

### Review 2 ###
Title: The minimax part is not a distraction

Thanks for all the comments and suggestions!
Yes - the paper is a bit overbearing and we understand that
you want us to simplify it. However Prop. 9 is not a minor
result. We will highlight this proposition more clearly.

>> "The authors define the minimax-optimal value in Definition 8 and provide some minor results in Prop 9."
>> "Such a ``minimax'' discussion acts as a distraction"
>> "make the paper less daunting (in terms of the number of results/lemmas)."
Reasons for keeping Prop. 9:
Almost all of the claims made in the paper are needed to obtain Prop. 9
and it provides BOTH upper and lower bounds for the minimax value Rk*. 
The bounds are tight up to within a constant factor. 
We will make this point clearer and the whole section more approachable in the final version.

+++MW: done

### Review 3 ###
Title: We have upper and lower bounds for the minimax value

>> "My major concern is with Sec. 1.2, and the so-called “minimax optimality” "
>> "For a typical paper, the next step would then be establishing matching upper and lower bounds of Rk*(X),"
BOTH upper and lower bounds for Rk* are given in Prop. 9 (part 2 and 3). 
The bounds are tight up to within a constant factor. 
In fact, the upper bound of C \phi/k (part 2) is a consequence of our main result, Theorem 4. 
Thus, while our main proposed estimator does not obtain exact minimax optimality 
(this appears very hard to attain), it does lead to a very strong guarantee for Rk*.

>> "The guarantees ... are additive, which are very different from the approximation
>> guarantees from Allen-Zhu et al. (2017), Wang et al. (2017) and Nikolov et al
>> (2018), deriving multiplicative guarantees."
>> "I feel this difference should be highlighted and discussed."
We completely agree. While we already point this out in the related work, we will highlight it further in the final version.
+++MW: not done
Dont know how to do this

>> "I suggest avoiding the usage of the term “minimax”, while replacing it with “minimum variance unbiased” "
>> "I suggest deriving some example scalings of \phi assuming X is randomly generated from some underlying distribution"
Good suggestions, thank you! We will address them in the final version.

### 2022-08-23 design/save/icml20/response.txt

We thank all the reviewers for their comments and feedback.

## To Reviewer #2

Thanks for the (updated) positive overall evaluation.

Motivation.
The CSSP is a well-established task in the literature, where the goal is *not* to replace SVD by a faster procedure, but rather to find a subset of columns that provides a good approximation of the matrix (e.g. for interpretability). SVD does not yield such a subset of columns. Many celebrated CSSP algorithms have been slower than the SVD, e.g., Boutsidis et al. (2011), Guruswami and Sinop (2012).

Runtime.
Our subset selection procedure is a standard k-DPP, which can be significantly faster than the cost of SVD. There are several almost-linear time k-DPP sampling algorithms, including by Deshpande and Rademacher (2010), Anari et al. (2016) and Derezinski et al. (2019).
 > "Alpha is defined through opt_k, which seems to require solving SVD "
Parameter alpha is only used in the analysis. It is *not* required for the algorithm.
 > "Even with carefully tuned concentration, aren’t a total number of $sqrt{k}$ trials needed before a size $k$ subset is returned?"
There are algorithms that sample directly from a k-DPP, e.g., Anari et al (2016), without repeated trials.

Metrics.
We agree that some approximation metrics for the CSSP and Nystrom may not exhibit multiple-descent peaks. Nevertheless, the approximation ratio we use is the most commonly used metric in the CSSP literature, and therefore precise understanding of its behavior is of great relevance to the community. We also believe that the multiple-descent curve is not unique to this metric.

Matern kernel.
The polynomial eigenvalue decay rate for the Matern kernel is discussed in Section 4.2 of Rasmussen and Williams (2006), see equation (4.15). These kernels are commonly studied, see, e.g., Burt et al (2019) and Mutny et al (2019).

## To Reviewer #4

Thanks for the thorough review, and the positive feedback on our technical contributions.

Connections to double descent.
We agree that the multiple descent curve in the CSSP exhibits important differences from the double descent phenomenon in the generalization error of over-parameterized ML models. We will clarify this in the final version to avoid any confusion.
We too are suspicious of papers that try to make a tenuous connection with a recently-popular topic, but in this case the connections are quite strong, and so we believe that our paper would be incomplete without mentioning double descent. We will make sure to clarify these connections (summarized below) in the final version.
 1. The peaks exhibited by the approximation ratio of the CSSP occur when the subset size k crosses a sharp drop in the spectrum of the data. Analogously, the double descent peak in linear regression occurs when the number of model features crosses the point where the spectrum of the design matrix drops to zero (i.e., the rank of that matrix; see Section 2 of Belkin et al, 2019b).
 2. Bartlett et al (2019) show that double descent can occur not only at the point where the spectrum drops to zero, but also when it exhibits a significant drop to a small non-zero value. Moreover, the notion of stable rank used in their analysis matches our notion (see line 109 of our submission). In other words, the peaks exhibited in the CSSP closely align with the peaks of the linear regression generalization error.
 3. Derezinski et al (2019b) provide an analysis of double descent for linear regression under DPP-based data distribution, and their analysis of the bias of the minimum norm solution leads to expressions that are closely related to our formulas for the CSSP error under DPP sampling (see line 258 of our submission).

 > "I would be interested to see more methods"
In Appendix F, we provide experimental results for the greedy selection method (instead of a k-DPP), which also exhibits the error peaks predicted by our analysis.

 > "The first regime of Remark 1 seems odd."
It is true that, in this regime, a non-negligible portion of the spectrum will not be recovered even by the best rank-k approximation. Nevertheless, this regime is still relevant for certain tasks, such as in applications to clustering, where k can be chosen independently of the data spectrum, for the sake of visualization or interpretability.

 > "In intro, ... would be worth citing the many results which give 1+epsilon bicriteria approximation."
We will address this in the final version.

 > "I think it should be justified a bit more why the focus is on the case of |S| = k."
Good point. Our results can also be applied to the setting where |S| > k, and we will address this in the final version.

 > "The definition of stable rank is a bit odd"
Our definition of stable rank (which is the same as in Definition 3 of Bartlett et al, 2019), sr_s(A), reduces to a commonly used definition of stable rank for s = 0. When s > 0, then this can be viewed as the stable rank of the matrix after removing top s singular vectors.
